Temperature and moisture effects on greenhouse gas emissions from deep active-layer boreal soils

### 2016-11-13 manuscript/cpcrw_manuscript.Rmd
Moved code from ms file to 5-analyze

```{r wc, echo=FALSE}
# Compute soil moisture data for use in abstract and results below
# wc and wc_alltrt are computed by 5-analyze.R script
gwcbegin <- subset(gwc_alltrt, stage == "Beginning")
gwcend <- subset(gwc, stage == "End")
gwcendmean <- gwcend$mean
names(gwcendmean) <- gwcend$Treatment
gwcendsd <- gwcend$sd
names(gwcendsd) <- gwcend$Treatment
vwcbegin <- subset(vwc_alltrt, stage == "Beginning")
vwcend <- subset(vwc_alltrt, stage == "End")
```

```{r compute_ratios, echo=FALSE}
# Compute ratios between CO2 and CH4 for use in abstract and results below
# Ratio data is stored in the `gas_ratio` d.f. computed by analysis script
minmag <- min(gas_ratio$CO2CH4_ratio) %>% log10 %>% floor %>%
  c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine")[.]
minratio <- min(gas_ratio$CO2CH4_ratio / 1e6)  %>% formatC(digits = 1, format = 'f')
mintrt <- gas_ratio$Treatment[which.min(gas_ratio$CO2CH4_ratio)]
mintemp <- gas_ratio$Temperature[which.min(gas_ratio$CO2CH4_ratio)]
maxratio <- max(gas_ratio$CO2CH4_ratio / 1e6) %>% formatC(digits = 1, format = 'f')
maxtrt <- gas_ratio$Treatment[which.max(gas_ratio$CO2CH4_ratio)]
maxtemp <- gas_ratio$Temperature[which.max(gas_ratio$CO2CH4_ratio)]
```

@@

```{r compute_excludes, echo=FALSE}
# Compute outlier and exclusion numbers
# TODO: this isn't good--fragile if files move or change names
rn <- readLines("../outputs/3-remove/removed_data.csv") %>% length
sdn <- readLines("../outputs/summarydata.csv") %>% length
fluxn <- nrow(fluxdata)
```

@@

```{r table1, echo=FALSE}
t1 <- summary(step_co2_lme)$tTable %>% round(3) %>% as.data.frame()
t1$`p-value` <- pclean(t1$`p-value`, printP = FALSE)
knitr::kable(t1, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```

@@

```{r table2, echo=FALSE}
t2 <- summary(step_co2_lme)$tTable %>% round(3) %>% as.data.frame()
t2$`p-value` <- pclean(t2$`p-value`, printP = FALSE)
knitr::kable(t2, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```

>>>>

@@

@@

```{r table1, echo=FALSE}
summary(step_co2_lme)$tTable %>% 
  round(3) %>% 
  as.data.frame() ->
  t1
t1$`p-value` <- pclean(t1$`p-value`, printP = FALSE)
knitr::kable(t1, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```

@@

```{r table2, echo=FALSE}
summary(step_co2_lme)$tTable %>% 
  round(3) %>% 
  as.data.frame() ->
  t2
t2$`p-value` <- pclean(t2$`p-value`, printP = FALSE)
knitr::kable(t2, digits = 3, col.names = c("Value", "SE", "DF", "T", "P"))
```
